\thesistitle

### 2019-07-19 sections/clonerefactor.tex
Removed the size as it's kind of useless
TODO stuff and new example table
Fixed some compilation warnings

As stated in the previous section, nodes in the graph link to \textit{preceding} cloned statement. This implies that the first node that is cloned does not have any clone relation, as there are no clones preceding it (only following it). Because of this, we start our clone detection process at the final location encountered while building the graph. For this node, we collect all nodes it is cloned with. Even though the final node only links to the preceding node it is cloned with, we can collect all clones. This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node. As an example, we convert the code example shown in figure \ref{fig:clonegraph} to a clone graph as displayed in figure \label{fig:clonegraph2}.

@@

Using the example shown in figure \ref{fig:clonegraph} and \label{fig:clonegraph2} we can explain how we detect clones on basis of this graph. Suppose we are finding clones for two files and the final node of the second file is a variable declarator. This final node is represented in the example figure by the purple box (1). We then follow all ``duplicate'' relations until we have found all clones of this node (2 and 3). We now have a single statement clone class of three clone instances (1, 2 and 3).

@@

\begin{table}[H]
\begin{center}
 \caption{The equality arrays in our example figure \ref{fig:equalityarrays}.} \label{table:equalityarrays}
 \medskip
\begin{tabular}{|l|l|l|}
\hline
Node (n) & Equality Array (E)     & Size (s) \\ \hline
1        & {[}1, -2, 3, -5, -6{]} & 5        \\ \hline
2        & {[}1, -2, 7, -5, -6{]} & 5        \\ \hline
3        & {[}1, -2, 4, -5, -6{]} & 5        \\ \hline
4        & {[}8, -2, 9, -5, -6{]} & 5        \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{equation}\label{eq:variabilityclonerefactor}
\frac{|\{x>0 \land y>0 \land x \neq y\text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{(s_1+s_2)+(s_3+s_4)}*100
\end{equation}

@@

\subsubsection{bla}

\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1) \exists (y \in E_2) x<0 \lor y<0 \Rightarrow x=y
\end{equation}

>>>>

As stated in the previous section, nodes in the graph link to \textit{preceding} cloned statement. This implies that the first node that is cloned does not have any clone relation, as there are no clones preceding it (only following it). Because of this, we start our clone detection process at the final location encountered while building the graph. For this node, we collect all nodes it is cloned with. Even though the final node only links to the preceding node it is cloned with, we can collect all clones. This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node. As an example, we convert the code example shown in figure \ref{fig:clonegraph} to a clone graph as displayed in figure \ref{fig:clonegraph2}.

@@

Using the example shown in figure \ref{fig:clonegraph} and \ref{fig:clonegraph2} we can explain how we detect clones on basis of this graph. Suppose we are finding clones for two files and the final node of the second file is a variable declarator. This final node is represented in the example figure by the purple box (1). We then follow all ``duplicate'' relations until we have found all clones of this node (2 and 3). We now have a single statement clone class of three clone instances (1, 2 and 3).

@@

\begin{table}[H]
\begin{center}
 \caption{The equality arrays in our example figure \ref{fig:equalityarrays}.} \label{table:equalityarrays}
 \medskip
\begin{tabular}{|l|l|l|}
\hline
Node (n) & Equality Array (E) \\ \hline
1        & {[}1, -2, 3, -5, -6{]} \\ \hline
2        & {[}1, -2, 7, -5, -6{]} \\ \hline
3        & {[}1, -2, 4, -5, -6{]} \\ \hline
4        & {[}8, -2, 9, -5, -6{]} \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{equation}\label{eq:variabilityclonerefactor}
\frac{|\{x>0 \land y>0 \land x \neq y\text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{(|E_1|+|E_2|)+(|E_3|+|E_4|)}*100
\end{equation}

@@

\subsubsection{Convert Equality Array to Graph}
\todo{TODO}
\begin{table}[H]
\begin{center}
 \caption{The equality arrays in our example figure \ref{fig:equalityarrays}.} \label{table:equalityarrays2}
 \medskip
\begin{tabular}{|l|l|l|}
\hline
Node (n) & Equality Array (E) \\ \hline
1        & {[}1, -2, 3, -5, -6{]} \\ \hline
2        & {[}1, -2, 3, -5, -6{]} \\ \hline
3        & {[}8, -2, 4, -5, -6{]} \\ \hline
4        & {[}1, -2, 7, -5, -6{]} \\ \hline
\end{tabular}
\end{center}
\end{table}

\subsubsection{Detect Clones on Graph}
\todo{TODO}
\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1) \exists (y \in E_2) x<0 \lor y<0 \Rightarrow x=y
\end{equation}

\subsubsection{Try to Expand}
\todo{TODO}
